The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update 'Ontological Architecture'

The \aw{} software (\cref{sec:aw}) is designed according to the three-ontology method~\citep{threeontologymethod}. 
This method is based on the interaction of a task ontology, a domain ontology and a top-level ontology. 
In our case, the ANNOdc plays the role of a task ontology and serves as the conceptual model of the software. 
One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) 
of the task ontology (ANNOdc), whereas the entities of the corresponding domain ontology (ANNOds) are processed dynamically. 
The \aw{} uses the ANNOdc as an interface to access the ANNOds entities, e.g. by listing all subclasses of a specific ANNOdc class, such as \aurl{anno}{Bone}, as described in \cref{sec:aw}.

>>>>

This architecture fits very well with the three-ontology method~\citep{threeontologymethod} on the basis of which we designed 
the \aw{} software (\cref{sec:aw}) for annotating human skeletons and determining phenotypes.
This method for developing consistent and modular software is based on the interaction of a task ontology, a domain ontology 
and a top-level ontology. In our case, the ANNOdc plays the role of a task ontology, while the ANNOds acts as a domain ontology. 
One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) 
of the task ontology, whereas the entities of the corresponding domain ontology are processed dynamically. 
The \aw{} uses the ANNOdc as an interface to access the ANNOds entities, e.g. by listing all subclasses of a specific ANNOdc class, 
such as \aurl{anno}{Bone}, as described in \cref{sec:aw}.
